COG-ED Manuscript

### 2022-02-14 06_Paper/COG-ED/Manuscript.Rmd
Update Manuscript.Rmd

In everyday life, effort and reward are closely intertwined [@Botvinick2009].
With each decision a person makes, they have to evaluate whether the effort required to reach a goal is worth being exerted, given the reward they receive when reaching the goal.
A reward is subjectively more valuable if it is obtained with less effort, so the required effort is used as a reference point for estimating the reward value [@Botvinick2009].
However, the cost of the effort itself is also subjective, and research has not yet established which function best describes the relationship between effort and cost [@Kool2018].
Investigating effort and cost is challenging because "effort is not a property of the target task alone, but also a function of the individual's cognitive capacities, as well as the degree of effort voluntarily mobilized for the task, which in turn is a function of the individual's reward sensitivity" [@Kool2018, p. 209].

One task that is often used to investigate effort is the n-back task, a working memory task in which a continuous stream of stimuli, e.g. letters, is presented on screen.
Participants indicate via button press whether the current stimulus is the same as *n* stimuli before, with *n* being the level of difficulty between one and six [@Mackworth1959].
The n-back task is well suited to investigate effort because it is an almost continuous manipulation of task load, as has been shown by monotonic increases in error rates, reaction times [@Jaeggi2010], and brain activity in areas associated with working memory [@Jonides1997; @Owen2005].
However, its reliability measures are mixed, and associations of n-back performance and measures such as executive functioning and fluid intelligence are often inconsistent [@Jaeggi2010].

>>>>

In everyday life, effort and reward are closely intertwined [@Botvinick2009].
With each decision a person makes, they have to evaluate whether the effort required to reach a goal is worth being exerted, given the reward they receive when reaching the goal.
A reward is subjectively more valuable if it is obtained with less effort, so the required effort is used as a reference point for estimating the reward value [@Botvinick2009].
However, the cost of the effort itself is also subjective, and research has not yet established which function best describes the relationship between effort and cost [@Kool2018].
Investigating effort and cost is challenging because "effort is not a property of the target task alone, but also a function of the individual's cognitive capacities, as well as the degree of effort voluntarily mobilized for the task, which in turn is a function of the individual's reward sensitivity" [@Kool2018, p. 209].
<!-- In the last sentence, the page number of the quote should appear with the quote, but given nature.csl does not, so perhaps just insert '(p. 209)' after 'reward sensitivity' -->

One task that is often used to investigate effort is the *n*-back task, a working memory task in which a continuous stream of stimuli, e.g. letters, is presented on screen.
Participants indicate via button press whether the current stimulus is the same as *n* stimuli before, with *n* being the level of difficulty between one and six [@Mackworth1959].
The *n*-back task is well suited to investigate effort because it is an almost continuous manipulation of task load as has been shown by monotonic increases in error rates, reaction times [@Jaeggi2010], and brain activity in areas associated with working memory [@Jonides1997; @Owen2005].
However, its reliability measures are mixed, and associations of *n*-back performance and measures such as executive functioning and fluid intelligence are often inconsistent [@Jaeggi2010].
